Generating Interactive WebSocket Applications in TypeScript

### 2020-03-12 PLACES_2020/abstract.tex
typo

In this paper, we present an implementation of the MPST framework for
developing interactive web applications using familiar industry tools using
TypeScript and the \textit{React.js} framework.
The developer can use the Scribble protocol
language to specify the protocol and use the Scribble toolchain to validate
and obtain the \emph{local protocol} for each role.
The local protocol describes the interactions of the global communication
protocol observed by the role.
We encode the local protocol into TypeScript types, catering for server-side
and client-side targets separately.
We show that our encoding guarantees that only implementations which conform to
the protocol can type-check.
We demonstrate the effectiveness of our approach through a web-based
implementation of the classic \textit{Noughts and Crosses} game from a MPST
formalism of the game logic.

>>>>

In this paper, we present an implementation of the MPST framework for
developing interactive web applications using familiar industry tools using
TypeScript and the \textit{React.js} framework.
The developer can use the Scribble protocol
language to specify the protocol and use the Scribble toolchain to validate
and obtain the \emph{local protocol} for each role.
The local protocol describes the interactions of the global communication
protocol observed by the role.
We encode the local protocol into TypeScript types, catering for server-side
and client-side targets separately.
We show that our encoding guarantees that only implementations which conform to
the protocol can type-check.
We demonstrate the effectiveness of our approach through a web-based
implementation of the classic \textit{Noughts and Crosses} game from an MPST
formalism of the game logic.

### 2020-03-12 PLACES_2020/conclusion.tex
typo

\section{Conclusion and Future Work}
We have presented a MPST-based framework for developing full-stack interactive
TypeScript applications with WebSocket communications.
The implementation conforms to a specified
protocol, statically providing linear channel usage guarantees and affine
channel usage guarantees for back-end and front-end targets respectively.

>>>>

\section{Conclusion and Future Work}
We have presented an MPST-based framework for developing full-stack interactive
TypeScript applications with WebSocket communications.
The implementation conforms to a specified
protocol, statically providing linear channel usage guarantees and affine
channel usage guarantees for back-end and front-end targets respectively.
